---
title: "togglr"
author: "Vincent Guyader"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{togglr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  eval= FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

## Installation of `togglr`


### From CRAN

```{r}
install.packages("togglr")
```


### From Github
```R
if (!require(devtools)){install.packages("devtools")}
devtools::install_github("ThinkR-open/togglr")
```



## Set toggl Api token

Go on toogl.com website : `https://toggl.com/app/profile` then select and copy your token api at the bottom of the page.

```{r}
set_toggl_api_token("your_token_api")
```
You just need to do this ones.


## Start the tracking system

Without any parameters it will create a new project using your Rstudio project names. 

```{r}
toggl_start()
```

By default the client name is "without client" you can choose (and eventualy create a client) by using :

```{r}
toggl_start(client = "my client")
```

But can also choose the task and the project

```{r}
toggl_start(client = "my client",
            description = "what I'm doing",
            project_name = "my project")
```


## Stop the tracking system

```{r}
toggl_stop()
```


## get total time passed on the current project

```{r}
get_project_task_detail()
get_current_duration()
```

## get all your dashboard

```{r}
get_dashboard()
```



## Some other uselfull function are in this package

```{r}
ls(package:togglr)
```

